### 2013-10-01 Paper_Markdown.Rmd
Began dividing data into Results section - some problems with plotting exist (really hard plots to make!). Changed bootstrap_wa to reconstruct July temperatures.

ggplot(data = data.frame(map), aes(long, lat)) + geom_path(aes(group=group), color='gray') +
  geom_point(data = data.frame(climate), aes(x = LONDD, y = LATDD), alpha = 0.5) +
  theme_bw() +
  xlab('') + ylab('') +
  theme(axis.text=element_text(size=12, family='serif')) +
  coord_map(projection='albers', lat0=30, lat1=50, xlim=c(-145, -60), ylim=c(26, 75))

@@

When we 
```{r MinMaxDissim, fig.width=7, fig.height=6, fig.cap='Figure: North American site locations'}

dissim.scores <- data.frame(dissim = c(min.diss, max.diss, as.vector(dists)),
                            class   = c(rep('Minimum', length(min.diss)),
                                        rep('Maximim', length(max.diss)), rep('All', length(as.vector(dists)))))

ggplot(dissim.scores) + 
  geom_density(aes(x = dissim, fill=class), alpha=0.5) +
  theme_bw() +
  xlab('Squared-chord Dissimilarity') +
  ylab('Density') +
  theme(text = element_text(size=24, family='serif'),
        strip.text = element_text(size=14, family='serif'),
        axis.text = element_text(size = 12, family='serif')) +
  scale_x_log10() + scale_y_sqrt()

@@

>>>>

ggplot(data = data.frame(map), aes(long, lat)) + 
  geom_polygon(aes(group=group), color='blue', alpha=0.2) +
  geom_point(data = data.frame(climate), aes(x = LONDD, y = LATDD), alpha = 0.5) +
  theme_bw() +
  xlab('') + ylab('') +
  theme(axis.text=element_text(size=12, family='serif')) +
  coord_map(projection='albers', lat0=30, lat1=50, xlim=c(-145, -60), ylim=c(26, 75))

@@

Results
=========================

When we examine the dissimilarity scores we can see that the distribution between minimum, maximum and overall dissimilarities can be understood numerically and spatially.

```{r MinMaxDissim, fig.width=7, fig.height=6, fig.cap='Figure: North American site locations'}

dissim.scores <- data.frame(dissim = c(min.diss, 
                                       max.diss, 
                                       as.vector(dists)[sample(length(dists), 10000)]),
                            class   = c(rep('Minimum', length(min.diss)),
                                        rep('Maximim', length(max.diss)), 
                                        rep('All', 10000)))

ggplot(dissim.scores) + 
  geom_density(aes(x = dissim, fill=class), alpha=0.5) +
  theme_bw() +
  xlab('Squared-chord Dissimilarity') +
  ylab('Density') +
  theme(text = element_text(size=24, family='serif'),
        strip.text = element_text(size=14, family='serif'),
        axis.text = element_text(size = 12, family='serif')) +
  annotate("segment", x=0.48, xend = -.32, y = 0, yend = 1, size=3, color='red') +
  scale_x_log10() + scale_y_sqrt()

@@

Model outputs
=========================
```{r LoadOutputs, echo=FALSE, message=FALSE, warning=FALSE}
load('data/wa.res.RData')
load('data/mat.res.RData')
load('data/wapls.res.RData')

vals <- c(seq(0, 0.2, by=0.001), seq(0.21, 1, by=0.01))

na.samples <- data.frame(size = as.vector(wa.res$sample_size),
                         distance = rep(vals, each = nrow(wa.res$sample_size)),
                         alpha.val = rep(diff(c(-.5,vals)), each = nrow(wa.res$sample_size))+0.005)

na.samples <- na.samples[!is.na(na.samples$size),]

ggplot(na.samples, aes(x=distance, y=size)) + geom_point(aes(alpha=alpha.val)) +
  xlab('Analogue Distance') + ylab('Available Samples') +
  theme(text = element_text(size=24, family='serif')) +
  theme_bw() +
  scale_alpha_identity(guide='none')

```
**Figure X**. *As the analogue distance exclusion is increased the available data set size is reduced, although some points continue to maintain a large number of potential analogues, this is directly related to the minimum distance to the closest analogue.  Points that maintain a large pool of analogues are far from neighbours.*

```{r PredictedValues, message=FALSE, echo=FALSE, warning=FALSE}

load('data/mat.res.RData')
load('data/wa.res.RData')
load('data/wapls.res.RData')

model.out <- data.frame(site   = rep(rep(climate[,1], ncol(mat.res$bias)),3),
                        preds  = c(as.vector(mat.res$mean_prediction),
                                   as.vector(wa.res$mean_prediction),
                                   as.vector(wapls.res$mean_prediction)),
                        dissim = rep(rep(vals, each=nrow(mat.res$bias)),3),
                        model  = rep(c('MAT', 'WA', 'WAPLS'), each = length(mat.res$bias)))

model.out <- model.out[!colSums(is.na(model.out)) > 0,]

ggplot(model.out, aes(x = dissim, y = preds, group = site)) +
  geom_path(alpha = 0.01) +
  theme_bw() +
  facet_wrap(~mode)
  scale_x_continuous(expand=c(0,0)) +
  annotate('segment', x=0, xend=1, 
           y=mean(climate[,10], na.rm=TRUE),
           yend=mean(climate[,10], na.rm=TRUE),
           color='red', size=1.5, linetype=2)

```
**Figure X**.
